oldmortality

### 2022-12-15 analyses/supportStudy.Rmd
re-analyzed

---
title: "Support"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 2
  layer1: 50
  layer2: 50
  layer3: 25
  layer4: 25
  drpt: 0.5
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
eval_support<-T
source_python('src/getSUP.py')
source_python("src/cIndex.py")
source_python("src/dsmScript.py")
source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
bsize=512
min_delta = 10^-7
epo=as.numeric(params$epo)
patience <- as.numeric(params$patience)
iteration<-as.numeric(params$iteration)
layer1<-as.numeric(params$layer1)
layer2<-as.numeric(params$layer2)
layer3<-as.numeric(params$layer3)
layer4<-as.numeric(params$layer4)
drpt<-as.numeric(params$drpt)

@@

#split training/testing
samp<-sample(seq(1,nrow(data),by=1), floor(nrow(data)*.80)) 
trainOG<-data[samp,]
test<-data[-samp,-c(ncol(data))]
fullTest<-data[-samp,,drop=F]

@@

  samp<-sample(seq(1,nrow(trainOG),by=1) , nrow(trainOG),replace = T) 
  train<-trainOG[samp,]
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 200
  )
  times<-times[-c(1,length(times))]

  ######################
  ###casebase + splines
  ######################
  mod_cb_glm <- fitSmoothHazard(status~bs(time)+.-time,
                                data = train,
                                time = "time",
                                event="status",
                                ratio = 100
  )

@@

  ######################
  ###DeepSurv
  ######################
  coxnn<-deepsurv(Surv(time, status) ~ .,data = train, frac = 0.2, activation = "relu",
                  num_nodes = c(layer1,layer2,layer3,layer4), dropout = drpt,
                  early_stopping = TRUE, epochs = epo,
                  batch_size = bsize,device = "cpu",best_weights=T,
                  patience = patience,min_delta=min_delta,batch_norm = F,
                  learning_rate = 0.001,lr_decay=10^-7)
  coxnnsurv<- predict(coxnn,newdata = test,type="survival")
  colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))

  ######################
  ###Deephit
  ######################
  source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epo,patience=patience,min_delta=min_delta,drpt=drpt)
  hitnnSurv<-t(hitnnSurv)
  colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)

  ######################
  ###PMNN splines
  ######################
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status"
  )

  fit<-fitSmoothHazSpline(pmnn,
                          epochs=epo,
                          batch_size=bsize,
                          verbose=0,
                          monitor="val_loss",
                          val_split=0.2,
                          min_delta=min_delta,
                          patience=patience)
  annPreds<-aarSplines(fit,
                       times=times,
                       x_test=test
  )
  rownames(annPreds)<-annPreds[,1]
  annProper<- t(annPreds[,-1])
  class(annProper)<-c("tunnel",class(annProper))

  ######################
  ###coxph
  ######################
  cox<-coxph(Surv(time, status) ~ ., data = train,x=T)

@@

  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status"
  )

  fit<-fitSmoothHaz(pmnn,
                    epochs=epo,
                    batch_size=bsize,
                    verbose=0,
                    monitor="val_loss",
                    val_split=0.2,
                    min_delta=min_delta,
                    patience=patience)
  annPreds<-aar(fit,
                times=times,
                x_test=test
  )

  rownames(annPreds)<-annPreds[,1]
  annProperpoly<- t(annPreds[,-1])
  class(annProperpoly)<-c("tunnel",class(annProperpoly))

  ######################
  ###IPA metric
  ######################
  brierFinalResults <- Score(list("Cox_Lin" = cox,'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,'DeepHit'=deephitCleaned,
                                  'PMNN_Spline'=annProper,'PMNN_Poly'=annProperpoly),
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score

  #######################
  ###Cox 
  ######################
  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))

@@

  tempTims<-   as.numeric(colnames(annProper))
  tempTims<-head(tempTims, -1)
  tempTims<-tail(tempTims, -1)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=length(riskList)+1)
  et_train<-as.matrix(train)[,c(16,15)]
  et_test<-as.matrix(fullTest[,c(16,15)])
  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'PMNN_Spline','PMNN_Poly')
  cScoreTemp[,1]<- tempTims

@@

>>>>

---
title: "Support"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 1
  layer1: 50
  layer2: 50
  layer3: 25
  layer4: 25
  drpt: 0.1
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
eval_support<-T
source_python('src/getSUP.py')
source_python("src/cIndex.py")
source_python("src/dsmScript.py")
source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
bsize=512
min_delta = 0#10^-7
epo=as.numeric(params$epo)
patience <- as.numeric(params$patience)
iteration<-as.numeric(params$iteration)
layer1<-as.numeric(params$layer1)
layer2<-as.numeric(params$layer2)
layer3<-as.numeric(params$layer3)
layer4<-as.numeric(params$layer4)
drpt<-as.numeric(params$drpt)

@@

#split training/testing

 spec = c(train = .7, test = .1, validate = .2)

 g = sample(cut(
   seq(nrow(data)), 
   nrow(data)*cumsum(c(0,spec)),
   labels = names(spec)
 ))

 res = split(data, g)

trainOG<-res$train

test<-res$test[,-c(ncol(data))]

fullTest<-res$test

val<-res$validate

valcb<-sampleCaseBase(data = val,time="time",event="status",ratio=100)
valcb$offset<-0
valcbtensor<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),as.matrix(valcb[,ncol(valcb),drop=F])),as.matrix(valcb[,ncol(valcb)-1,drop=F]))

  times<-seq(from=min(test$time)+0.000001,
             to=max(test$time)-0.000001,
             length.out = 100
  )

@@

  samp<-sample(seq(1,nrow(trainOG),by=1) , nrow(trainOG),replace = T) 
  train<-trainOG[samp,]
  sds<-sapply(train, function(x) (sd(x)))
means<-sapply(train, function(x) (mean(x)))
test<-normalizer(res$test,means,sds)[,-c(ncol(data))]
fullTest<-normalizer(res$test,means,sds)
val<-normalizer(res$validate,means,sds)

train<-normalizer(train,means,sds)

  #########################
  ###casebase+splines
 ##########################
    mod_cb_glm <- fitSmoothHazard(status~bs(time)+.-time,
                                data = train,
                                time = "time",
                                event="status",
                                ratio = 100
  )

@@

  # 
  # 
  # ############################
  # ###DeepSurv
  # ############################

  source_python('src/dsurv.py')
  #need to break ties
  tiebreakTrain<-train

  #while(length(unique(tiebreakTrain$time))/length(tiebreakTrain$time)!=1 ){
  #tiebreakTrain<-train
  #tiebreakTrain$time<-tiebreakTrain$time+runif(nrow(tiebreakTrain),0,1/10000000000)
  #}

  coxnnsurv=fitDeepSurv(tiebreakTrain,fullTest,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lay3=layer3,lay4=layer4)
  coxnnsurv<-t(coxnnsurv)
  #colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-times#seq(0,1,length.out = ncol(cnnCleaned))
  py_run_string("del fitDeepSurv")
  rm(fitDeepSurv)

  # coxnn<-deepsurv(Surv(time, status) ~ .,data = train, frac = 0.2, activation = "relu",
  #                 num_nodes = c(layer1,layer2,layer3,layer4), dropout = drpt,
  #                 early_stopping = TRUE, epochs = epo,
  #                 batch_size = bsize,device = "cpu",best_weights=T,
  #                 patience = patience,min_delta=min_delta,batch_norm = F,
  #                 learning_rate = 0.001,lr_decay=10^-7)
  # 
  # coxnnsurv<- predict(coxnn,newdata = test,type="survival")
  # colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  # cnnCleaned<-pyProcess(coxnnsurv,times=times)
  # colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))
  ############################
  ###Deephit
  ############################  
    source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lay3=layer3,lay4=layer4)
  hitnnSurv<-t(hitnnSurv)
  #colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)
  # source_python('src/deephitter.py')
  # hitnnSurv=fitDeephit(train,fullTest,bsize,epo,patience=patience,min_delta=min_delta,drpt=drpt)
  # hitnnSurv<-t(hitnnSurv)
  # colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  # deephitCleaned<-pyProcess(hitnnSurv,times=times)
  # colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  # py_run_string("del fitDeephit")
  # rm(fitDeephit)
  # 
  ############################
  ###PMNNsplines
  ############################  
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",optimizer=optimizer_adam(learning_rate = 0.0001)
  )

  fit<-fitSmoothHazSpline(pmnn,
                          epochs=epo,
                          batch_size=bsize,
                          verbose=0,
                          monitor="val_loss",
                          #val_split=0.2,
                          min_delta=min_delta,
                          patience=patience,val=valcbtensor)

   annPreds<-aarSplines(fit,
                       times=times,
                       x_test=test
  )
  rownames(annPreds)<-annPreds[,1]
  annProper<- t(annPreds[,-1])
  class(annProper)<-c("tunnel",class(annProper))

  ############################
  ###coxph
  ############################  
  cox<-coxph(Surv(time, status) ~ ., data = train,x=T)

@@

  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",optimizer=optimizer_adam(learning_rate = 0.0001)
  )

  fit<-fitSmoothHaz(pmnn,
                    epochs=epo,
                    batch_size=bsize,
                    verbose=0,
                    monitor="val_loss",
                    val_split=0.2,
                    min_delta=min_delta,
                    patience=patience,val=valcbtensor)
  annPreds<-aar(fit,
                times=times,
                x_test=test
  )

  rownames(annPreds)<-annPreds[,1]
  annProperpoly<- t(annPreds[,-1])
  class(annProperpoly)<-c("tunnel",class(annProperpoly)) 
  ############################
  ###Brier Score
  ############################

  brierFinalResults <- Score(list("Cox_Lin" = cox,
                                  'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,
                                  'DeepHit'=deephitCleaned,
                                  'PMNN_Spline'=annProper,
                                  'PMNN_Poly'=annProperpoly),
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score
    ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
  geom_line()+coord_cartesian(ylim=c(-0.1,0.2))
  ######################
  ###Cox
  ######################
  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))

@@

  tempTims<-   as.numeric(colnames(annProper))
  tempTims<-head(tempTims, -1)
  tempTims<-tail(tempTims, -1)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=length(riskList)+1)
  et_train<-as.matrix(train)[,c(16,15)]
  et_test<-as.matrix(fullTest[,c(16,15)])
  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'PMNN_Spline','PMNN_Poly')#,'dsm')
  cScoreTemp[,1]<- tempTims

@@

  ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
  geom_line()+coord_cartesian(ylim=c(-0.1,0.2))

### 2022-12-15 analyses/timevaryingOldMortality.Rmd
re-analyzed

---
title: "oldmortality"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 1
  layer1: 50
  layer2: 20
  layer3: 25
  layer4: 25
  drpt: 0.1
---

@@

preData<-data.frame(sex=oldmort$sex,
                 civ=oldmort$civ,
                 ses=oldmort$ses.50,
                 birthplace=oldmort$birthplace,
                 ageAtEntry=oldmort$enter,
                 imrAtBirth=oldmort$imr.birth,
                 region=oldmort$region,
                 birthdate=oldmort$birthdate,
                 time=oldmort$exit-oldmort$enter,
                 status=as.numeric(oldmort$event))

preData$time<-preData$time+runif(nrow(preData),0,1)/100000000

@@

 spec = c(train = .75, test = .10, validate = .15)

@@

trainOG<-res$train

@@

@@

  samp<-sample(seq(1,nrow(trainOG),by=1) , nrow(trainOG),replace = T) 
  train<-trainOG[samp,]
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 200
  )
  times<-times[-c(1,length(times))]

@@

  #while(length(unique(tiebreakTrain$time))/length(tiebreakTrain$time)!=1 ){
  #tiebreakTrain<-train
  #tiebreakTrain$time<-tiebreakTrain$time+runif(nrow(tiebreakTrain),0,1/10000000000)
  #}

@@

   print('starting cbnnsplines')
  ######################
  ###PMNN splines
  ######################
  ###########################################
###########################################
  valcbtensor[[1]][[2]]<-rep(mod_cb_glm$offset[1],nrow(valcbtensor[[1]][[1]]))
###########################################  
###########################################  
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>%
    layer_dense(units=layer1,use_bias = T)%>%
    layer_batch_normalization()%>%
    activation_tanh()%>%
    layer_dropout(drpt)%>%

    layer_dense(units=layer2,use_bias = T)%>%
    layer_batch_normalization()%>%
    activation_tanh()%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)#%>%activation_tanh()

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",
                  optimizer=optimizer_adam(learning_rate = 0.001)#,decay=10^-7)
  )

@@

  covars_output<-covars_input%>%

    layer_dense(units=20,use_bias = T)%>%
     layer_batch_normalization()%>%
    activation_relu()%>%
    layer_dropout(drpt)%>%

    layer_dense(units=10,use_bias = T)%>%

    activation_relu()%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

>>>>

---
title: "oldmortality"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 1
  layer1: 200
  layer2: 20
  layer3: 25
  layer4: 25
  drpt: 0.1
---

@@

omor=as.data.frame(matrix(NA,nrow=length(unique(oldmort$id)),ncol=ncol(oldmort)))
colnames(omor)<-colnames(oldmort)
unique(oldmort$id)[1]
j<-1
for(i in 1:length(unique(oldmort$id))){
  temp<-which(oldmort$id %in% unique(oldmort$id)[i])
  if(length(temp)==1){
  omor[j,]<-oldmort[temp,]
  j<-j+1
  }else if(length(temp)>=1){
    tempData<-oldmort[which(oldmort$id %in% unique(oldmort$id)[i]),]
    omor[j,]<-tempData[which.min(tempData$enter),]
    #omor[j,]$exit<-max(tempData$exit)
    j<-j+1
  }

}

oldmort<-omor
preData<-data.frame(sex=as.factor(oldmort$sex),
                 civ=as.factor(oldmort$civ),
                 ses=as.factor(oldmort$ses.50),
                 birthplace=as.factor(oldmort$birthplace),
                 ageAtEntry=oldmort$enter,
                 imrAtBirth=oldmort$imr.birth,
                 region=as.factor(oldmort$region),
                 birthdate=oldmort$birthdate,
                 time=oldmort$exit-oldmort$enter,
                 status=as.numeric(oldmort$event))

#preData$time<-preData$time+runif(nrow(preData),0,1)/100000000

@@

 spec = c(train = .70, test = .10, validate = .20)

@@

trainOG<-

@@

sds<-sapply(trainOG, function(x) (sd(x)))
means<-sapply(trainOG, function(x) (mean(x)))

normalizer<-function(data,means,sds){
  normalized<-data
  for (i in 1:ncol(data)){
    normalized[,i]<-(data[,i]-means[i])/sds[i]
  }
  normalized$status<-data$status
  normalized$time<-data$time
  return(normalized)
}

test<-normalizer(res$test,means,sds)[,-c(ncol(data))]
fullTest<-normalizer(res$test,means,sds)
val<-normalizer(res$validate,means,sds)

trainOG<-normalizer(res$train,means,sds)

@@

  samp<-sample(seq(1,nrow(trainOG),by=1) , nrow(trainOG),replace = T) 
  train<-trainOG[samp,]
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 100
  )
  times<-times[-c(1,length(times))]

@@

  while(length(unique(tiebreakTrain$time))/length(tiebreakTrain$time)!=1 ){
  tiebreakTrain<-train
  tiebreakTrain$time<-tiebreakTrain$time+runif(nrow(tiebreakTrain),0,1/10000000)
  }

@@

   print('starting cbnnsplines')
  ######################
  ###PMNN splines
  ######################
  ###########################################
###########################################
  valcbtensor[[1]][[2]]<-rep(mod_cb_glm$offset[1],nrow(valcbtensor[[1]][[1]]))
###########################################  
###########################################  
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>%layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T)%>%
   # layer_batch_normalization()%>%
    activation_tanh()%>%
    layer_dropout(drpt)%>%

    layer_dense(units=layer2,use_bias = T)%>%
    #layer_batch_normalization()%>%
    activation_tanh()%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)#%>%activation_tanh()

@@

  covars_output<-covars_input%>% layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T)%>%
   # layer_batch_normalization()%>%
    activation_tanh()%>%
    layer_dropout(drpt)%>%

    layer_dense(units=layer2,use_bias = T)%>%
    #layer_batch_normalization()%>%
    activation_tanh()%>%
    layer_dropout(drpt)%>%

    layer_dense(units=1,use_bias = T)#%>%activation_tanh()

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",
                  optimizer=optimizer_adam(learning_rate = 0.0001)
  )
